---
output:
  html_document: default
  keep_tex: yes
  word_document: default
  pdf_document: default
---

##CDN-Yukon harvest-diversity simulations
`r Sys.Date()`

```{r setup, include=FALSE}
source("Load.R")
# set harvest rate and border passage goals for alternative policies
  t_harvest_rate <- seq(0,1,length.out=40) # range of US target commercial harvest rates
  BPG <- seq(1,100000,length.out=40) # range of border passage goals
  
  pol.1x<-45000; pol.1x.ind <- which(abs((BPG)-pol.1x)==min(abs((BPG)-pol.1x)))
  pol.1y<-0.2; pol.1y.ind <- which(abs((t_harvest_rate)-pol.1y)==min(abs((t_harvest_rate)-pol.1y)))
  
  pol.2x<-20000; pol.2x.ind <- which(abs((BPG)-pol.2x)==min(abs((BPG)-pol.2x)))
  pol.2y<-0.8; pol.2y.ind <- which(abs((t_harvest_rate)-pol.2y)==min(abs((t_harvest_rate)-pol.2y)))

# load simulation output
  outcomes <- readRDS("./outputs/base_sims.ricker")
  
  outcomes.med <- apply(outcomes,c(1,2,3),quantile,probs=c(0.5),na.rm=T)
  outcomes.upper <- apply(outcomes,c(1,2,3),quantile,probs=c(0.75),na.rm=T)
  outcomes.lower <- apply(outcomes,c(1,2,3),quantile,probs=c(0.25),na.rm=T)

# a 40 x 10 x 40 array (BPG x PMs X Target_us_harvest)

```

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

```{r  fig1, echo=FALSE,fig.height = 7.75, fig.width = 9.75, fig.align = "center"}
par(mfrow=c(3,3),bty="o", mar=c(2,2,2,5),oma=c(2,2,1,1))

# panel a - escapement
  xx<-as.table((outcomes.med[,1,]/1000))
  colnames(xx)<-((t_harvest_rate))
  rownames(xx)<-((BPG/1000))
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1]))
  y <- as.numeric(paste(long.data[,2]))
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000), y = (t_harvest_rate)))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000)
  yy<-(t_harvest_rate)
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",col=rev(viridis(100)))
    axis(1,labels=F)
    axis(2,las=2)
    mtext("(a) Escapement (000s fish)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)

#panel b - harvest
  xx<-as.table((outcomes.med[,2,]/1000))
  colnames(xx)<-((t_harvest_rate))
  rownames(xx)<-((BPG/1000))
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1]))
  y <- as.numeric(paste(long.data[,2]))
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000), y = (t_harvest_rate)))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000)
  yy<-(t_harvest_rate)
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",col=rev(viridis(100)))
    axis(1,labels=F)
    axis(2,las=2,labels=F)
    mtext("(b) Harvest (000s fish)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)

#panel c - harvest rate
  xx<-as.table(outcomes.med[,3,]*100)
  colnames(xx)<-((t_harvest_rate) )
  rownames(xx)<-((BPG/1000) )
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1])) 
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  zz[zz <0] =0 
  zz[zz >100] =100 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",zlim=c(0,100))
    axis(1,labels=F)
    axis(2,las=2,labels=F)
    mtext("(c) Harvest rate (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,zlim=c(0,100),col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)

#panel d - overfished
  xx<-as.table(outcomes.med[,4,]*100)
  colnames(xx)<-((t_harvest_rate) )
  rownames(xx)<-((BPG/1000) )
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1])) 
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  zz[zz <0] =0 
  zz[zz >100] =100 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",zlim=c(0,100))
    axis(1,las=1,labels=F)
    axis(2,las=2)
    mtext("(d) Stocks overfished (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,zlim=c(0,100),col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)
  
#panel e - extirpated
  xx<-as.table(outcomes.med[,6,]*100)
  colnames(xx)<-((t_harvest_rate) )
  rownames(xx)<-((BPG/1000) )
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1])) 
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  zz[zz <0] =0 
  zz[zz >100] =100 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",zlim=c(0,100))
    axis(1,las=1,labels=F)
    axis(2,las=2,labels=F)
    mtext("(e) Populations extirpated (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,zlim=c(0,100),col=viridis(100),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)

#panel f - CV
  xx<-as.table(1/outcomes.med[,9,])
  colnames(xx)<-((t_harvest_rate))
  rownames(xx)<-((BPG/1000))
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1]))
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="")
    axis(1,at=c(0,40,80,120,160),labels=F)
    axis(2,las=2,labels=F)
    mtext("(f) Harvest stability (1/CV)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,col=rev(viridis(100)),legend.width = 2)
    box(col="black")
    
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)
  
#panel g - meet CDN FN needs
  xx<-as.table(outcomes.med[,8,]*100)
  colnames(xx)<-((t_harvest_rate))
  rownames(xx)<-((BPG/1000))
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1]))
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="")
    axis(1)
    axis(2,las=2)
    mtext("(g) Chances CDN FN harvest met (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)

#panel h - meet US sub needs
  xx<-as.table(outcomes.med[,7,]*100)
  colnames(xx)<-((t_harvest_rate))
  rownames(xx)<-((BPG/1000))
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1]))
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="")
    axis(1)
    axis(2,las=2,labels=F)
    mtext("(h) Chances US subsistence met (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)
  

#panel i - trib goals
  xx<-as.table(outcomes.med[,10,]*100)
  colnames(xx)<-((t_harvest_rate) )
  rownames(xx)<-((BPG/1000) )
  long.data <- as.data.frame(xx)
  x <- as.numeric(paste(long.data[,1])) 
  y <- as.numeric(paste(long.data[,2])) 
  z <-as.numeric(long.data[,3])
  data.loess = loess(z~x*y)
  grid = expand.grid(list(x = (BPG/1000) , y = (t_harvest_rate) ))
  zz<-as.matrix(predict(data.loess, newdata = grid))
  xx<-(BPG/1000) 
  yy<-(t_harvest_rate) 
  zz[zz <0] =0 
  zz[zz >100] =100 
  
  image(xx,yy,zz,axes=F,ylab="",xlab="",zlim=c(0,100))
    axis(1,las=1)
    axis(2,las=2, labels = F)
    mtext("(i) Chance tributary goals met (%)",3,cex=0.9,line=0.5,adj=0)
  image.plot(xx,yy,zz,axes=F,add=T,legend.mar=3,zlim=c(0,100),col=rev(viridis(100)),legend.width = 2)
    box(col="black")
  
  points(pol.1x/1000,pol.1y,pch=21,cex=2.2,bg="grey",lwd=2)
  text(pol.1x/1000,pol.1y,"1",cex=0.8)


mtext("Border passage goal (000s)",1,outer=T,cex=1.1,lin=0.75)
mtext("US commercial harvest rate (%)",side=2,outer=T,cex=1.1,line=0.75)
```
Figure 1. **Predicted consequences of alternative harvest policies**. Each policy is defined by a combination of basin scale harvest (y-axis) and escapement goals (x-axis). Performance measures (z-axis) are calculated over the last 20 years of each Monte Carlo trial (500 in total), which project stock dynamics 50 years forward in time, and correspond to (A) median harvest (in thousands of Chinook salmon), (B) harvest stability (1/ coefficient of variation [CV] in harvest), (C) proportion of sub-stock tributaries with spawner abundances that exceeded a tributary specific spawner target (S~MSY~) and (D) proportion of sub-stocks extirpated. Three illustrative harvest policies are overlaid on each panel: (1) a policy that seeks to maximize yield, (2) a fixed harvest policy corresponding to minimum subsistence needs and (3) a policy that seeks to reduce biological risks to sub-stocks while also achieving relatively high harvests. 

```{r  fig2, echo=FALSE,fig.height = 5, fig.width = 9, fig.align = "center"}

# extract two constrasting policies and associated PMs
pol.1 <- cbind(rep("pol_1",10),
               c("Escapement", 
                 "Harvest",
                 "Harvest rate",
                 "Overfished (%)", 
                 "% pred. extrinct",
                 "Extirpated (%)",
                 "Chances US subsistence met (%)",
                 "Chances CDN FN harvest met (%)",
                 "Harvest stability (1/CV)",
                 "Trib. goals met (%)"),
               outcomes.med[pol.1x.ind,,pol.1y.ind],
               outcomes.upper[pol.1x.ind,,pol.1y.ind],
               outcomes.lower[pol.1x.ind,,pol.1y.ind])

pol.2 <- cbind(rep("pol_2",10),
               c("Escapement", 
                 "Harvest",
                 "Harvest rate",
                 "Overfished (%)", 
                 "% pred. extrinct",
                 "Extirpated (%)",
                 "Chances US subsistence met (%)",
                 "Chances CDN FN harvest met (%)",
                 "Harvest stability (1/CV)",
                 "Trib. goals met (%)"),
               outcomes.med[pol.2x.ind,,pol.2y.ind],
               outcomes.upper[pol.2x.ind,,pol.2y.ind],
               outcomes.lower[pol.2x.ind,,pol.2y.ind])

pms <- as.data.frame(rbind(pol.1[-5,],pol.2[-5,]))
colnames(pms)<-c("policy","performance_measure","med","upper","lower")

for(i in 3:5){pms[,i] <- as.numeric(as.character(pms[,i]))}

ggplot(pms,aes(x=policy, y=med))+
  facet_wrap(~performance_measure, scales = "free_y")+
  geom_col(fill=c(rep(c("#440154FF","#FDE725FF"),9)))+
  geom_errorbar(aes(ymin=lower,ymax=upper), width=0)+
  xlab("Policy")+
  ylab("")+
  theme_bw()
```
Figure2. **Harvest policy performance**. 